Transfer of Value Functions via Variational Methods

### 2018-05-18 NIPS 2018/main.tex
Completed appendix revision

For the maze navigation task in Section~\ref{sec:mn}, here we enumerate the mazes that were designed to realize the experiments. In Figure~\ref{fig:mazes}, there are $20$ mazes with varying degree of difficulty and that were designed to hold some similarities that would be useful for transferring. Moreover, we ensure $4$ groups of mazes that are characterized by their goal position.

For the experiments we use as an approximator an MLP with two hidden layers of $32$ neurons with ReLU as activation functions..For training the sources we use DDQN with a \textit{Batch size} of $70$, a \textit{Buffer Size} of $10000$ and a \textit{Target Update Frequency} of $100$, setting the \textit{Exploration Fraction} to $0.1$ and learning rate to $\alpha=0.001$.

In transfer experiments we use $\psi=0.5$, a \textit{Batch Size} of $50$, a \textit{Buffer Size} of $50000$ and use $10$ sampled \textit{weights} from the posterior to approximate the TD error. Moreover, we use $\lambda=10^{-6}$. For GVT, in particular, we use $\alpha_{\mu}=0.001$ as the rate to learn the mean parameters of our Gaussian posterior. For the Cholesky factor L, instead, we use $\alpha_{L}=10^{-7}$ and set the minimum value reachable by its eigenvalues to be $\sigma_{min}=0.0001$. In the case of MGVT experiments we set $\alpha_{\mu}=0.001$ to learn the mean of the different Gaussian components of our posterior and set $\alpha_{L}=10^{-6}$ for the Cholesky factors of its covariances. Finally, we use $\sigma_p^2=10^{-5}$ as the prior variance.

@@

In Figure~\ref{}, we present the results of transferring from $5$ source tasks to the mazes shown in Figure~\ref{fig:maze0}, Figure~\ref{fig:maze6}, Figure~\ref{fig:maze8} and Figure~\ref{fig:maze13} using \todo{also GVT?} GVT and MGVT. We show both the evaluation reward, i.e. the average performance obtained evaluating the mean parameters of the posterior in a given iteration of the algorithm by following a greedy policy w.r.t. those parameters, and the expected return. All the curves result from averaging $20$ independent runs and randomly sampled sources.

@@

Hereafter, we present additional results of transferring from $5$ source tasks to the mazes shown in Fig. \ref{fig:maze0}, Fig. \ref{fig:maze6} and Fig. \ref{fig:maze13} using both GVT and MGVT. We show both the evaluation performance, i.e. the average performance obtained evaluating the mean parameters of the posterior in a given iteration of the algorithm by following a greedy policy w.r.t. those parameters, and the expected return during the learning process. All the curves result from averaging $20$ independent runs and randomly sampled sources.

>>>>

The mazes adopted in the experiments of Sec. \ref{} are shown in Fig.~\ref{fig:mazes}. Our $20$ mazes have with varying degree of difficulty and are designed to hold few similarities that would be useful for transferring. Moreover, we ensure $4$ groups of mazes that are characterized by their goal position.

For the experiments we use as an approximator an MLP with two hidden layers of $32$ neurons with ReLU activation functions. For training the sources we use a DDQN with a \textit{batch size} of $70$, a \textit{buffer size} of $10000$ and a \textit{target update frequency} of $100$, setting the \textit{exploration fraction} to $0.1$ and learning rate to $\alpha=0.001$.

In the transfer experiments we use $\psi=0.5$, a \textit{batch size} of $50$, a \textit{buffer size} of $50000$ and use $10$ sampled \textit{weights} from the posterior to approximate the TD error. Moreover, we use $\lambda=10^{-6}$. For GVT, in particular, we use $\alpha_{\mu}=0.001$, $\alpha_{L}=10^{-7}$, and set the minimum value reachable by its eigenvalues to be $\sigma_{min}=0.0001$. In the case of MGVT, we set $\alpha_{\mu}=0.001$ and $\alpha_{L}=10^{-6}$. Finally, we use $\sigma_p^2=10^{-5}$ as the prior bandwidth.

@@

@@

Hereafter, we present additional results of transferring from $5$ source tasks to the mazes shown in Fig. \ref{fig:maze0}, Fig. \ref{fig:maze6} and Fig. \ref{fig:maze13} using both GVT and MGVT. We show both the greedy and online performances. All the curves result from averaging $20$ independent runs and randomly sampled sources.
